The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents

### 2024-02-11 starter_folder-main/paper/paper.qmd
total change
script 2 change

#import data
raw_data_full <-
  read_csv(
    file = "../data/analysis_data/combined_cleaned_data.csv",
    show_col_types = FALSE)
```

@@

```
```{r}
#| label: fig-one
#| fig-cap: Scatter Plot of Agression versus Hostile Offline Scores 
#| echo: false

@@

```{r}
#| label: fig-two
#| fig-cap: Scatter Plot of Agression versus Hostile Online Scores 
#| echo: false

@@

```{r}
#| label: fig-three
#| fig-cap: Scatter Plot of Agression versus Hostile Online Scores Minus Hostile Offline Scores
#| echo: false

@@

>>>>

#import data
raw_data_full <-
  read_csv(
    file = "../data/analysis_data/combined_cleaned_data.csv",
    show_col_types = FALSE)

raw_data_full <-
  read_csv(
    file = "../data/as_data/combined_cleaned_data.csv",
    show_col_types = FALSE)
```

@@

```
```{r}
#| label: fig-one
#| fig-cap: Scatter Plot of Agression versus Hostile Offline Scores 
#| echo: false
#| message: false

@@

```{r}
#| label: fig-two
#| fig-cap: Scatter Plot of Agression versus Hostile Online Scores 
#| echo: false
#| message: false

@@

```{r}
#| label: fig-three
#| fig-cap: Scatter Plot of Agression versus Hostile Online Scores Minus Hostile Offline Scores
#| echo: false
#| message: false

@@

```{r}
#| label: fig-tab-two
#| fig-cap: Scatter Plot of Agression versus Hostile Online Scores Minus Hostile Offline Scores
#| echo: false
#| message: false

####Calculate the t-test result between Online and Offline hostile score
t_test_onoff <- t.test(raw_data_full$hostile_online, raw_data_full$hostile_offline)
t_test_onoff
